A review on Generative Learning in Computer Vision

### 2020-05-08 paper.tex
added 3dgan

\subsubsection{3D-GAN}

>>>>

\subsubsection{3D-GAN}
3D-GAN, is a 3D-object generation GAN proposed by Wu et al \cite{b8} in 2016. This was a novel technique which focused on the 3D space generation using GAN using CNN. 3D object generation is not an easy task due to the high-dimensionality of the object. With high dimensionality, a large number of parameters are needed. To solve this high dimensionality problem, CNN is the best bet out there. A CNN with the apropriate configuration helps in increasing the dimensions of the sample space while also being able to reduce the parameters/features. The authors proposed a CNN which is similar to DCGAN. With this architecture they have managed to reduce the features by a great amount. They added a Sigmoid layer in the end. Due to the fact that it is difficult to generate a 3D object as compared to be able to classify them, the authors had to come up with a simple training method. They used a bigger batch with very low learning rate. This method proved to be able to generate good-quality shapes.
